\section{Conclusion}
Based on a ruby on rails framework, with jQuery libraries, building up a web server is not simple as what we see. In order to make a good product, we need to familiar with font end design technologies(html, CSS, JavaScript). Especially all the new technologies are born quickly, vast solutions and enormous tools appear. Even sometimes, it will be a little hard to struggle with the latest techniques and run after time, but keep a positive attitude to face the new things and get the capacity to filter the important information in such a big data era would be the key to success. In addition, script programming, knowledge of database and network, all of them are the basic elements to construct the final building. A wide view of multi-domains will facilitate the innovation.

Personally I am quite satisfied with what I had done. Every one or two weeks, a new feature was added, in other words, I got many different experience every one or two weeks. But also I discover the importance of test and management of project. The quality is much more important than the quantity. A few stable functions will be much better than a lot features which could not work. Further, the tests play a really important role in the development, before this internship, I thought the test time could not more than the development, it could only reach half of the whole period, but in the reality, the developers always pass most of time to check. What's more, it is impressive to work with kind and smart people in such a beautiful country. 

A full stack engineer is not only an expert in a domain, but also should be familiar with different fields, then be capable to adapt to different environment and be capable to work under pressure. This internship not only allow me to learn much more scientific technologies, but also a good experience to be a responsible engineer.