% passage aux conventions typologiques anglaises

\section*{Abstract}
The automation becomes the main melody in the new innovation era. The appearance of autonomous vehicle, unmanned drones and ships accelerate the robotization process. With this innovate engine, many derivative services and applications are born to control and optimize the planning. The WRSC (World Sailing Robotic Championship) follows the similar trace. The championship demonstrates the academic researches in the autonomous sailing robots to prospect the near future. 

Under this background, it is indispensable to build a reliable tracking system to supervise the path of sailing robots. This paper introduces the development of the tracking system for the WRSC 2015 during my summer internship at Åland University of Applied Sciences. Especially, this paper aims to describe the ruby on rails framework based development of the new web site with several changes in GUI, account security management, automatic scoring and ranking differed with the previous web sites

  
\section*{Keywords}
WRSC 2015, ruby on rails, web site, automatic scoring and ranking

% retour aux conventions françaises


\section*{Résumé}
  Dans le cadre de ses fonctions, l'ingénieur se doit de maîtriser les
  techniques de base de rédaction de documents.

  Le présent guide fournit les premiers éléments visant à la rédaction d'un
  rapport de projet. Il est destiné aux élèves effectuant un projet dans le
  cadre de leur scolarité à l'\gls{enstab}.  Sont présentés, de façon
  synthétique, les bases sur la nature et la structure du rapport, ses règles
  de composition et de typographie.

\section*{Mots clés}
WRSC 2015, ruby on rails, web site, automatic scoring and ranking




%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../guide"
%%% End: 
